### 2021-07-07 rad-icfp-2021/relwork.tex
some related work

\noindent \textbf{More array primitives}
filter, flatten, gather, scanl, ...
can be derived by hand once and then it's ok

\noindent \textbf{Recursion}
TODO

\noindent \textbf{Higher derivatives}
TODO

\noindent \textbf{Sparse data and matrix representation}
TODO

@@

\noindent \textbf{Usage of iteration mechanics}
A immense effort in machine learning for the past decade has been in finding
good architectures, to limit computational costs, 
avoid vanishing and exploding gradients, 
and have better building blocks of large complicated systems than traditional layers of a neural network.
Different approaches 
(Dynamic neural networks \cite{jin2017manipulability,wu2016deep}, 
Recursive NN \cite{socher2011parsing,biancofiore2017recursive}, 
Reccurent NN \cite{bahdanau2014neural,luong2015effective}, 
Tree LSTM \cite{tai2015improved,chen2016enhanced}, 
Dynamic Recursive NN \cite{guo2019dynamic}, 
Top-down Tree LSTM \cite{zhang2015top}, 
Recursion in DNN \cite{jeong2018improving}) 
have found that recursive data structures such as trees are good candidates.
We have emphasized here on differentiating fold left on arrays for efficiency, 
but one should be able to adapt this on any algebraic data type. 
It will be interesting to see if and how we recover efficient backpropagation on the proposed architectures 
which is usually derived by hand and one main goal of these papers.

>>>>

\noindent \textbf{More array primitives}
We focused on giving reverse derivatives for a small set of array primitives. 
Other common primitives include filter, flatten, gather. 
These functions can easily be added to our Source language once we provide a reverse derivative for them.
This is reminiscent of hand-crafted derivatives present in large AD frameworks (usually hundreds), 
and these can already be added in added in our language. 
One only needs to make sure that the provided transpose Jacobian is correct.

\noindent \textbf{Recursion}
It would be an interesting extension to our work to see if one can define efficient pure reverse derivatives on general recursion.

\noindent \textbf{Higher derivatives}
There are recent approaches to computing higher derivatives using jets \cite{betancourt2018geometric} which generalise forward and reverse mode.
A more standard approach is to iterate forward or reverse-mode. 
Forward mode is standard and can easily be defined on our Target language. 
As our optimization procedure removes lambdas, to iterate reverse-mode we would only need to compute reverse derivatives for the new primitives of Target, that is !scanl, scanr, shift1L, shift1R!.

@@

\noindent \textbf{Usage of iteration mechanics}
An immense effort in machine learning for the past decade has been in finding
good architectures, to limit computational costs, 
avoid vanishing and exploding gradients, 
and have better building blocks for large complicated systems than traditional layers of a neural network.
Different approaches 
(Dynamic neural networks \cite{jin2017manipulability,wu2016deep}, 
Recursive NN \cite{socher2011parsing,biancofiore2017recursive}, 
Reccurent NN \cite{bahdanau2014neural,luong2015effective}, 
Tree LSTM \cite{tai2015improved,chen2016enhanced}, 
Dynamic Recursive NN \cite{guo2019dynamic}, 
Top-down Tree LSTM \cite{zhang2015top}, 
Recursion in DNN \cite{jeong2018improving}) 
have found that recursive data structures such as trees are good candidates.
We have emphasized here on differentiating fold left on arrays for efficiency, 
but one should be able to adapt this on any algebraic data type. 
It will be interesting to see if and how we recover efficient backpropagation on the proposed architectures 
which is usually derived by hand and one main goal of these papers.
